\textbf{Brief Document On the Hall C Hodoscopes Calibration}

### 2020-04-08 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

The trigger setup for this experiment required a minimum of 3/4 hodoscope planes to detect a signal for data readout in each spectrometer. Due to the absence of significant background and the low
accidental trigger rates at the higher missing momentum settings, the use of additional particle identification (PID) was found to have little to no effect on the final cross section.\\

@@

\indent The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$

@@

\indent The experimental and theoretical reduced cross 

@@

\noindent sections were extracted and are defined as follows:

@@

\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,

@@

is a recoil factor obtained by integrating over the deuteron binding energy in the 6-fold differential cross section, and $\sigma_{\mathrm{cc1}}$ is the

>>>>

For each spectrometer, a logical hardware signal was created from  the coincidence of hits in three of the four scintillator planes. The event trigger was the the coincidence of these two signals. \\

@@

\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$

@@

@@

\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section, $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,

@@

is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the

### 2020-04-08 MY_THESIS/Hodoscope_Calib_Doc/hodo_calib.tex
updated

  \caption{Cartoon of individual scintillator paddles to illustrate the various timing corrections applied. (Graph Source: E. Pooser)}

@@

  which causes the dscriminated logic signal to jitter in time, when it should \textbf{NOT}, since the signals arrived at the

@@

  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time. (See Figure \ref{fig:TWFit}) The function that is currently
  being used in Hall C has the form:
    f_{TW}(a) = c_{1} + \frac{1}{(\frac{a}{TDC_{Thrs.}})^{c_{2}}}
  where $a$ is the ADC amplitude,  $TDC_{Thrs}$ is the TDC threshold which is currently set to 120 mV. \newpage

>>>>

  \caption{Cartoon of individual scintillator paddles to illustrate the various timing corrections applied.}

@@

  which causes the discriminated logic signal to jitter in time, when it should \textbf{NOT}, since the signals arrived at the

@@

  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time.
